---
title: "Carrie_Assigment4"
output: html_notebook
---

#2. Loading packages
```{r}
library(tidyverse)
library (ggthemes)
```

#3. importing data
```{r}
assignment4 = read_csv("a4_data.csv")
```

#4. Rows and columns
```{r}
nrow(assignment4) 
ncol(assignment4) 
#There are 3700 rows and 12 columns in this data file
```

# 5. Unique participants & trials
```{r}
#unique participants
assignment4 %>% 
pull (subject) %>% 
unique()
#There are 37 unique subjects

#trials
assignment4 %>%
group_by(subject) %>%
count()
#Each subject did 100 trials
```

#6. Levels of variables
```{r}
assignment4 = assignment4 %>%
mutate(prime_condition=as.factor(prime_condition))
assignment4 = assignment4 %>%
mutate(state = as.factor(state))
levels(assignment4 %>% pull(prime_condition))
levels(assignment4 %>% pull(state))
```
#prime_condition has 4 levels: :both", "phonological", "semantic", and "unrelated" 
#state has 4 levels: "dontknow", "know", "other", and "tipoftongue"

#7. Subsets of columns
```{r}
prime_information=
assignment4 %>%
select(subject, prime_condition)
```

#8. Subsets of rows
```{r}
phonological=
assignment4 %>%
  filter(prime_condition=="phonological" & accuracy==1)
```

#9. Summarizing accuracy per subject
```{r}
subject_acc=
assignment4 %>%
group_by(subject) %>%
summarize(mean_acc=mean(accuracy))
```

#10. Summarizing accuracy per prime condition
```{r}
prime_acc=
assignment4 %>%
group_by(prime_condition) %>%
summarize(mean_acc=mean(accuracy),
          sd_acc=sd(accuracy))
```

#11. Histogram of subject accuracy
```{r}
subject_acc %>%
ggplot(aes(x=mean_acc))+geom_histogram(binwidth=0.2, fill="brown", color='black', position = "identity")+theme_few()+labs(x='mean accuracy', y='count', title='histogram of mean accuracy')
```

#12. Bar plot of prime condition
```{r}
prime_acc %>%
ggplot(aes(x=prime_condition, y=mean_acc))+geom_bar(fill="pink", color='navy', stat='identity')+theme_few()+labs(x='prime condition', y='mean accuracy', title='Mean accuracy across prime condition')
```
#13. Data interpretation
#According to the bar graph, the mean accuracy in different prime conditions does vary. The mean accuracy is the highest in phonological condition and the lowest in the semantic condition.  

#Extra credit
#14. Summarizing accuracy per prime condition and state
```{r}
state_prime_acc=
assignment4 %>%
group_by(state, prime_condition) %>%
summarize(mean_acc=mean(accuracy))
```

#15. Bar plot of prime condition and state
```{r}
state_prime_acc %>%
ggplot(aes(x=prime_condition, y=mean_acc, fill=state)) + geom_col(position="dodge") + theme_few() + labs(x="prime condition", y="mean accuracy", title="Mean accuracy across prime condition and reported states")
```

